\section*{Abstract}
\setstretch{1.5}
The Life Tracker web app is a transformative digital tool designed to address the challenges faced by individuals in today's fast-paced world. With the ever-increasing demands of modern life and the constant influx of digital distractions, people often struggle to manage their tasks, prioritize goals, and maintain a healthy balance between work and personal well-being. Our project aims to provide a holistic solution by seamlessly integrating three core components: to-do lists, prompted journals, and digital detox features. In this project, we recognize the need for a comprehensive platform that not only helps users stay organized but also fosters self-reflection and encourages healthier digital habits. The Life Tracker app empowers users to create and manage tasks efficiently, set reminders, and establish priorities. The prompted journals feature prompts users to express gratitude, set intentions for personal growth, and track progress. Additionally, the digital detox function allows users to set limits on digital interactions, ensuring a more mindful use of technology. The project's scope includes customization options to tailor the app to individual preferences, making it a personalized and empowering tool. Our methodology involves the development of a user-friendly interface, integration of seamless features, and emphasis on data privacy and user security. By offering a holistic approach to task management, self-reflection, and digital detox, the Life Tracker app aims to positively impact users' lives, helping them achieve higher productivity, better work-life balance, and a more mindful and fulfilling daily routine.

\par
\vspace{0.5}
\textbf{Keywords:} \textit{ Productivity, Task Management, To-Do Lists, Prompted Journals, Digital Detox}