\pagenumbering{arabic}
\section{INTRODUCTION}
\setstretch{1.5}
\subsection{Background}

The rapid advancement of technology has revolutionized the way we manage tasks, communicate, and engage with the world. However, this digital revolution has also introduced new complexities. The constant influx of information, the all time presence of digital devices, and the challenges of maintaining a work-life equilibrium have become increasingly prevalent. The "Life Tracker" app draws inspiration from this background, seeking to provide users with a unified platform that serves to their user's needs for organization, encourages self-reflection, and fosters a balanced relationship with digital technology. The project ’Life Tracker’ is an automated system designed to optimize
your productivity, promote digital detox, and foster personal growth.
The main objective of this productivity system is to provide structured approach
of doing tasks and much needed self-reflection to people who in to-
day’s fast- paced world often find themselves juggling multiple responsibilities, tasks, and commitments. This system empowers users to track their
achievements, gain insights, and make meaningful improvements to reach
their full potential.
This software is a web-based application and can be hosted on the Internet.
It also provides a clean and user-friendly interface to the users.

\subsection{Problem Statement}
The current digital landscape forces user to have a limited attention span and lack of direction. Individuals struggle with juggling their tasks, find almost no time for personal reflection, and have a hard time fighting against the negative impacts of excessive digital exposure. Existing productivity apps may address certain aspects but fail to provide a comprehensive solution that takes into account the inter-connectedness of productivity, self-awareness, and digital balance. The challenge lies in creating an integrated solution that supports users in enhancing their productivity, fostering personal growth, and promoting healthy digital habits.



\subsection{Scope}
The scope of the Life Tracker app encompasses three core components: to-do lists, prompted journals, and digital detox. The app will enable users to create and manage tasks efficiently, set reminders, and establish priorities. The prompted journals will encourage users to engage in regular self-reflection, express gratitude, and set intentions for personal growth. The digital detox feature will empower users to set limits on digital interactions, thereby helping them strike a healthier balance between their online and offline lives. The app's scope also includes personalized customization options to align with individual preferences and goals.\\

\newpage
\subsection{Objective}

\begin{itemize}
    \item To develop a unified app for integrating task management, reflective journaling and digital detox features to enhance productivity.

  
\end{itemize}
