
\section{LITERATURE REVIEW}
The landscape of productivity and well-being apps has expanded significantly, offering specialized solutions for various aspects of daily life. Task management tools, streamline to-do lists, reflective journaling apps promote self-awareness and personal growth, and digital detox aids counter excessive screen time. While each of these systems serves crucial roles, they often lack a holistic approach that addresses the complete needs of individuals, leaving room for a more comprehensive solution. We aim to address this need by offering a unified solution that empowers individuals to lead more organized, purposeful, and fulfilling lives in today's digital landscape.
\subsection{Existing}

\begin{itemize}
    \item \textbf{Todoist}\\
    Todoist is a popular task management application that empowers users to create, organize, and prioritize their to-do lists efficiently. It offers features such as setting task deadlines, priorities, and repetitions, allowing individuals to stay organized and on track with their daily tasks. While Todoist excels in task management, it may lack certain elements that cater to the holistic needs of users, such as reflective journaling and mechanisms for managing digital distractions.

    \item \textbf{Day One}\\
    Day One is a reflective journaling app that encourages users to document their thoughts, experiences, and personal growth. It provides a valuable platform for individuals to reflect on achievements, challenges, and aspirations, fostering self-awareness. However, Day One primarily focuses on the reflective aspect and may not include task management features or digital detox mechanisms, leaving a potential gap in addressing the comprehensive needs of users.

    \item \textbf{Forest}\\
    Forest is a digital detox app designed to combat the adverse effects of excessive digital engagement. It encourages users to limit screen time by using gamified methods like planting virtual trees. This approach helps individuals regain focus and reduce distractions, contributing to a more mindful use of technology. However, Forest primarily concentrates on mitigating digital overuse and may not include features for task management or reflective journaling, potentially missing elements needed for a well-rounded solution.
\end{itemize}
\vspace{0.5in}
\subsection{Proposed}

In this proposed project, the "Life Tracker" web app addresses challenges posed by technology's rapid advancement, aiming to serve as a unified platform for users' organizational needs, self-reflection, and balanced digital interaction.

The project recognizes the complexities introduced by the digital revolution, including information overload and the constant presence of digital devices. The primary objective is to create an automated system that optimizes productivity, promotes digital detox, and fosters personal growth, catering to individuals who juggle multiple responsibilities.

The app, accessible through a clean and user-friendly web interface, integrates to-do lists, prompted journals, and digital detox features. It empowers users to manage tasks efficiently, engage in self-reflection, and achieve a healthier digital-life equilibrium. Overall, the "Life Tracker" project aims to offer a comprehensive solution that enhances productivity, nurtures personal growth, and promotes mindful technology usage in today's fast-paced digital era.

\subsubsection{Functional Requirements}
\begin{itemize}
    \item  Users can create, edit, and delete tasks each having a description, priority, and deadline.
   \item Users can mark tasks as completed.
\item Users can create and edit journal entries each containing content and timestamps.
   \item Users can specify website restrictions for digital detox.
   \item Users can activate and deactivate digital detox mode.
\end{itemize}


\subsubsection{Non-functional Requirements}
\begin{itemize}
    \item The app's user interface must be intuitive and easy to navigate.

    \item Tasks, journal entries, and settings must be organized for quick access.

    \item 
User authentication and data storage must be secure.
\end{itemize}
